A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add NP-completeness notice of improving the variable ordering

Nevertheless, all lower bounds for $n$-bit integer multiplication are exponential
in the number of nodes. Especially because of the high practical relevance of
$n$-bit integer multiplication this is one of the main drawbacks of the OBDD
representation~\cite{BRYANT86, BRYANT91, WOELFEL01}. \tbr

>>>>

Nevertheless, all lower bounds for $n$-bit integer multiplication are exponential
in the number of nodes. Especially because of the high practical relevance of
$n$-bit integer multiplication this is one of the main drawbacks of the OBDD
representation~\cite{BRYANT86, BRYANT91, WOELFEL01}.

Another topic researchers put much effort into was the variable ordering problem.
Section~\ref{subsec:dynamic-variable-ordering} already described one possible
approach to this problem but there are many other approaches such as heuristics
and simulated annealing algorithms~\cite{BOLLIG96}.

Bollig and Wegener~\cite{BOLLIG96} studied the complexity of improving the
variable ordering. They investigated this problem by analyzing the following
problem: Given an OBDD representing $f$ and a size bound $s$. Does an OBDD exist,
also representing $f$ and respecting an arbitrary variable ordering, having at
most $s$ nodes? "Unfortunately", they were able to prove this problem to be 
NP-complete. Hence, improving the variable ordering of OBDDs is
NP-complete~\cite{BOLLIG96}. \tbr
